### 2018-04-19 experiments.tex
fixups

def psplit(P):
    return ([P,1.0-P])
@>
\vspace{0.1in}
pool: <P> 3
pool: <cpts> 3
pool: <evidence> 3 OPAQUE
pool: <ename> 3
pool: <event> 3
\vspace{0.1in}
<P> := 0.01 * <[0..100]>
\vspace{0.1in}
<ename> := "E" + str(<[1..5]>)
\vspace{0.1in}
\{Exception\} <event> := [datarray.DataArray(psplit(<P>), axes = [<ename>])]
\{Exception\} <ename,1>!=<ename,2> -> <event> := [datarray.DataArray([[psplit(<P>)],psplit(<P>)],[<ename>,<ename>])]
\vspace{0.1in}
<cpts> := []
~<cpts>.append(<event>[0])
\vspace{0.1in}
<evidence> := \{\}
~<evidence>.update([(<ename>,0)])
\vspace{0.1in}
\{Exception\} print(flatten\_and\_sort(inference\_algs.calc\_marginals\_simple(<cpts>,<evidence>)))
\{Exception\} print(flatten\_and\_sort(inference\_algs.calc\_marginals\_sumproduct(<cpts>,<evidence>)))
\{Exception\} print(flatten\_and\_sort(inference\_algs.calc\_marginals\_jtree(<cpts>,<evidence>)))
\end{code}
}
\caption {Complete TSTL harness for finding the hash-order bug in the datarray
  inference algorithms.}
\label{hashbug}
\end{figure*}

@@

The TSTL harness for {\tt pyfakefs} has been used to detect (and
correct) over 50 faults.  However, the testing completely relies on
the existence of a reference file system implementation.  One purpose
of failure nondeterminism is to make it somewhat easier to perform
property-based testing of
complex APIs like this even without a reference implementation, or in cases
where (as is common, e.g. in file system development at NASA
\cite{ICSEDiff,CFV08}) the implementations do not use the same error
codes, making checking of behavior of failing calls more problematic.

>>>>

def psplit(P):
    return ([P,1.0-P])
@>
\vspace{0.1in}
pool: <P> 3
pool: <cpts> 3
pool: <evidence> 3 OPAQUE
pool: <ename> 3
pool: <event> 3
\vspace{0.1in}
<P> := 0.01 * <[0..100]>
<ename> := "E" + str(<[1..5]>)
\{Exception\} <event> := [datarray.DataArray(psplit(<P>), axes = [<ename>])]
\{Exception\} <ename,1>!=<ename,2> -> <event> := [datarray.DataArray([[psplit(<P>)],psplit(<P>)],[<ename>,<ename>])]
<cpts> := []
~<cpts>.append(<event>[0])
<evidence> := \{\}
~<evidence>.update([(<ename>,0)])
\vspace{0.1in}
\{Exception\} print(flatten\_and\_sort(inference\_algs.calc\_marginals\_simple(<cpts>,<evidence>)))
\{Exception\} print(flatten\_and\_sort(inference\_algs.calc\_marginals\_sumproduct(<cpts>,<evidence>)))
\{Exception\} print(flatten\_and\_sort(inference\_algs.calc\_marginals\_jtree(<cpts>,<evidence>)))
\end{code}
}
\caption {Complete TSTL harness for finding the hash-order bug in the datarray
  inference algorithms.}
\label{hashbug}
\end{figure*}

@@

The TSTL harness for {\tt pyfakefs} has been used to detect (and
correct) over 50 faults.  However, the testing completely relies on
the existence of a reference file system implementation.  One purpose
of failure nondeterminism is to make it somewhat easier to perform
property-based testing of
complex APIs like this even without a reference implementation, or in cases
where (as is common, e.g. in file system development at NASA
\cite{ICSEDiff,CFV08}) the implementations do not use the same error
codes.

### 2018-04-19 implementation.tex
fixups

\begin{table*}
\centering
{%\scriptsize

\caption{TSTL Method Calls for Nondeterminism Detection}
\label{tab:methods}
\begin{tabular}{l|l}
%\hline
Name & Purpose \\
\hline
\hline
{\tt nondeterministic} & returns True if test exhibits final state nondeterminism in $k$
  tries with delay $d$\\
\hline
{\tt stepNondeterministic} & as above, except checks all visible values
                       (compares state at every step)\\
\hline
{\tt processNondeterministic} & as above, except runs test provided in
                          subprocess and compares non-opaque output
                          values \\
\hline
{\tt P} & returns probability that a predicate holds for a test (with
          optional number of sample to use in estimate) \\
\hline
{\tt forceP} & wraps a predicate for test reduction (e.g. {\tt
         nondeterministic}) with desired probability of holding,
         sample size,\\
&  and replications required \\
\hline
\hline

@@

\begin{table*}
\centering
{%\scriptsize
\caption{TSTL Command Line Options for
  Nondeterminism Detection}
\label{tab:options}
\begin{tabular}{l|l|l}
%\hline
Name &  Tool(s) & Purpose \\
\hline
\hline
{\tt --checkDeterminism} & {\tt rt}, {\tt reduce} & Checks tests for deterministic
                                  behavior (visible value in rt, final
  value in reduce)\\
\hline
{\tt --checkProcessDeterminism} & {\tt rt}, {\tt reduce} & Checks determinism using more 
                                         expensive process-changed 
                                         execution \\
\hline
{\tt --determinismTries INT} & {\tt rt}, {\tt reduce} & Number of times to repeat test 
                                  checking for nondeterministic
                                  behavior \\
\hline 
{\tt --determinismDelay FLOAT} & {\tt rt}, {\tt reduce} & Delay between steps when 
                                  re-executing to check for
                                              determinism \\
\hline 
{\tt --checkFailureDeterminism} & tstl compiler & Produce a harness
                                                  that checks
                                                  determinism on all
                                                  failing actions \\
\hline 
{\tt --probability P} & {\tt reduce} & force property with respect to which 
                               test is being reduce to hold with 
                                 probability $P$ \\
\hline 
{\tt --samples S} & {\tt reduce} & use $S$ samples when checking predicate
                             probability\\
\hline 
{\tt --replications R} & {\tt reduce} & use $R$ replications when checking predicate probability\\
\hline
\hline

>>>>

\begin{table*}
\centering
{\scriptsize

\caption{TSTL Method Calls for Nondeterminism Detection}
\label{tab:methods}
\begin{tabular}{l|l}
%\hline
Name & Purpose \\
\hline
\hline
{\tt nondeterministic} & returns True if test exhibits final state nondeterminism in $k$
  tries with delay $d$\\
\hline
{\tt stepNondeterministic} & as above, except checks all visible values
                       (compares state at every step)\\
\hline
{\tt processNondeterministic} & as above, except runs test provided in
                          subprocess and compares non-opaque output
                          values \\
\hline
{\tt P} & returns probability that a predicate holds for a test (with
          optional number of sample to use in estimate) \\
\hline
{\tt forceP} & wraps a predicate for test reduction, checking that it
               has desired probability of holding, using
         sample size and replications parameters \\
\hline
\hline

@@

\begin{table*}
\centering
{\scriptsize
\caption{TSTL Command Line Options for
  Nondeterminism Detection}
\label{tab:options}
\begin{tabular}{l|l|l}
%\hline
Name &  Tool(s) & Purpose \\
\hline
\hline
{\tt --checkDeterminism} & {\tt rt}, {\tt reduce} & Checks tests for deterministic
                                  behavior (visible value in rt, final
  value in reduce)\\
\hline
{\tt --checkProcessDeterminism} & {\tt rt}, {\tt reduce} & Checks determinism using more 
                                         expensive process-changed 
                                         execution \\
\hline
{\tt --determinismTries INT} & {\tt rt}, {\tt reduce} & Number of times to repeat test 
                                  checking for nondeterministic
                                  behavior \\
\hline 
{\tt --determinismDelay FLOAT} & {\tt rt}, {\tt reduce} & Delay between steps when 
                                  re-executing to check for
                                              determinism \\
\hline 
{\tt --checkFailureDeterminism} & tstl compiler & Produce a harness
                                                  that checks
                                                  determinism on all
                                                  failing actions \\
\hline 
{\tt --probability P} & {\tt reduce} & force property with respect to which 
                               test is being reduce to hold with 
                                 probability $P$ \\
\hline 
{\tt --samples S} & {\tt reduce} & use $S$ samples when checking predicate
                             probability\\
\hline 
{\tt --replications R} & {\tt reduce} & use $R$ replications when checking predicate probability\\
\hline
\hline
